\title{Back to the Fraktur}

%\section{Question/topic}
Apart from decorative use in wine labels, newspaper mastheads, and tattoos, you rarely see Fraktur nowadays. We've become unaccoustomed to the letterforms, and it takes some effort to even get through a few paragraphs of modernized Fraktur. If you want to read old texts you also have to get used to old conventions. It's my hope that this text will make you better prepared to take on reading Fraktur.

Let's start with looking at some lower case letters:

\beginblockquote
{\UnifrakturMaguntiaXVI a b c d e f g h i j}
\endblockquote



\section{Letterforms new and old}
- Lower case modern forms

- Upper case modern forms

- Older forms

- Rules % cufflink

\section{Contemporary use}

{ 
It does no harm to print a Christmas card in black letter, but who nowadays would read a book in that type? I may believe, as I do, that black letter is in design more homogenous, more lively and more economic a type than the grey round roman we use, but I do not now expect people to read a book in it. Aldus\null' and Caslon's are both relatively feeble types, but they represent the forms accepted by the community; and the printer, as a servant of the community, must use them, or one of their variants. No printer should say, 'I am an artist, therefore I am not to be dictated to. I will create my own letter forms', for, in this humble job, no printer is an artist in this sense.

\rightline{--Stanley Morison}}

\section{History}
- Culture and politics of the alphabet: the will to unify or break out. 

Qinzhuang, Rome, Charlemagne, Soviet Union.

- Maximilian I to Hitler?

\vfil\break

\section{Opentype features}

Emphasis - letterspace (8), Schwabacher

ss01 - modern forms (cv00 – cv10, cv20)

ss02 - U/u becomes V/v at beginning of words, v becomes u in the middle

cv00 - no long s, only round s

cv01 - modern k, ck ligature

cv02 - modern x

cv03 - modern y

cv04 - modern A

cv05 - modern G

cv06 - modern K

cv07 - Modern N

cv08 - Modern S

cv09 - Modern V

cv10 - Modern Y

cv11 - long s heuristic

cv12 - round r after round letter (+hlig for tironian etc)

cv13 - I and J both written J

ss03 - i becomes j at beginning of word, j becomes i in the middle

cv14 - uc two letter umlauts (eg. Ae)

cv15 - lc umlaut e

cv16 - suppress deswash with diacritical mark

cv17 - diacritics over long s

cv19 - emdash instead of endash

cv20 - deswash s in middle of words

cv21-25 - diacritics over letters with swashes etc

lnum - "normal numbers" historically accurate

onum - more fraktur looking numbers, not historically accurate

dlig - macron bar m or n instead of mm nn

\vskip 2\baselineskip
◊ UnifrakturMaguntia16: cv11, cv12, cv13, cv14, cv15, cv19, hlig, lnum, ss02

◊ UnifrakturMaguntia17: cv11, cv13, cv14, cv15, cv19, hlig, lnum, ss02

◊ UnifrakturMaguntia18: cv11, cv13, cv14, cv15, cv19, hlig, lnum

◊ UnifrakturMaguntia19: cv11, cv13, cv14, cv19, hlig, lnum

◊ UnifrakturMaguntia20: cv11, cv19, lnum

◊ UnifrakturMaguntia21: ss01
